### 2017-07-27 Paper01_EnthalpyAndCrystallization.tex
Fixed DSC Bulk table values
DSC Table - added film onsets table
Method - worked on XRD and DSC

\subsection{\acrshort{dsc} characterization}
Isochronic DSC (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under protective argon atmosphere. Scans were performed at heating rates of 5 to 100 K/min.

@@

The temperature was raised in 5 K increments at 20 K/min. scans of xx over a range of 31 - 60 2 theta allows 20 minute scans.

@@

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
		$K/min$ & & & & & & \\
		\midrule
		100 & 136.1 & 163.4 & 205.2 & 217.2 & 251.2 & 270.6 \\ 
		80 & 132.0 & 159.5 & 201.5 & 213.7 & 245.3 & 266.0 \\ 
		60 & 129.6 & 157.4 & 199.1 & 210.9 & 240.6 & 261.8 \\ 
		40 & 126.6 & 155.0 & 196.3 & 208.0 & 234.8 & 256.3 \\ 
		30 & 126.2 & 151.1 & 193.7 & 204.8 & 230.5 & 252.3 \\ 
		20 & 125.1 & 149.8 & 190.9 & 201.4 & 224.1 & 247.5 \\ 
		15 & 123.8 & 148.5 & 189.2 & 199.3 & 220.7 & 244.4 \\ 
		10 & 123.5 & 144.7 & 186.1 & 195.9 & 215.4 & 240.2 \\ 
		5 & 120.5 & 141.7 & 181.9 & 189.8 & 204.5 & 232.8 \\ 
		\bottomrule
	\end{tabular}
	\caption{Bulk \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}. All temperatures are in \degree C.}
	\label{tab:BulkOnsets}
\end{table}

>>>>

\subsection{\acrshort{dsc} characterization}
Isochronic DSC (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under protective argon atmosphere. Scans were performed at heating rates of 5 to 100 K/min. Film samples were deposited directly into the pan. For annealing XRD samples DSC samples were heated to desired temperature at 20 K/min and then quenched to room temperature before the XRD measurements.

@@

The temperature was raised in 5 K increments at 20 K/min. Scans from 31 - 60 2 theta were completed within 1092 seconds (18min 12sec) to minimise the effects of recrystallisation.

@@

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
		$K/min$ & & & & & & \\
		\midrule
		100 & 136.1 & 152.4 & 193.4 & 201.8 & 240.2 & 262.4 \\
		80  & 132.0 & 151.6 & 194.4 & 201.9 & 238.2 & 260.3 \\
		60  & 129.6 & 151.6 & 190.0 & 197.8 & 232.9 & 259.0 \\
		40  & 126.6 & 151.0 & 189.0 & 200.0 & 226.4 & 254.7 \\
		30  & 126.2 & 147.4 & 187.0 & 198.4 & 221.0 & 251.1 \\
		20  & 125.1 & 147.3 & 188.4 & 197.0 & 216.0 & 246.8 \\
		15  & 123.8 & 146.0 & 186.2 & 195.6 & 212.2 & 243.9 \\
		10  & 123.5 & 142.3 & 183.4 & 192.9 & 207.4 & 239.8 \\
		5   & 120.5 & 139.2 & 179.7 & 187.5 & 199.8 & 232.7 \\ 
		\bottomrule
	\end{tabular}
	\caption{Bulk \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}. All temperatures are in \degree C.}
	\label{tab:BulkOnsets}
\end{table}

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
		$K/min$ & & & & & & \\
		\midrule
		100 & 108.5 & 135.1 & 0.0 & 177.3 & 0.0 & 240.3 \\
		80  & 106.0 & 128.2 & 0.0 & 165.6 & 0.0 & 238.8 \\
		60  & 107.3 & 129.1 & 0.0 & 176.1 & 0.0 & 237.8 \\
		40  & 100.2 & 117.6 & 0.0 & 170.7 & 0.0 & 234.2 \\
		30  & 95.3  & 114.4 & 0.0 & 169.5 & 0.0 & 232.5 \\
		20  & 95.5  & 110.0 & 0.0 & 170.5 & 0.0 & 229.4 \\
		15  & 92.5  & 107.4 & 0.0 & 168.8 & 0.0 & 224.0 \\
		\bottomrule
	\end{tabular}
	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}. All temperatures are in \degree C.}
	\label{tab:DSCOnsets}
\end{table}
